Fusion of Mass Spectrometry and Raman Spectroscopy Data

### 2025-06-13 dev/dev_statistics.Rmd

The individual processing steps are applied according to *ProcessingSettings*. Below, the integration of the TIC is shown using the dedicated *ProcessingSettings* after loading the TIC chromatograms from the analysis files and smoothing using a moving average approach.

@@

```{r}
# Smoothing of the TIC chromatogram for improving peak finding
ms$smooth_chromatograms(Settings_smooth_chromatograms_movingaverage(windowSize = 5))
```

```{r}
# Settings for integration of the TIC
ps_ic <- Settings_integrate_chromatograms_StreamFind(
  merge = TRUE,
  closeByThreshold = 5,
  minPeakHeight = 3E6,
  minPeakDistance = 3,
  minPeakWidth = 20,
  maxPeakWidth = 200,
  minSN = 5
)

@@

According to the MS1 spectra, the *m/z* from 1200 to 2000 can be added to the dedicated *ProcessingSettings* for deconvolution, as shown below. The first step is to load from the mzML files the traces within the retention time and *m/z* ranges selected.

@@

# ms$cluster_spectra(Settings_cluster_spectra_StreamFind(val = "mz", clustVal = 0.01, presence = 0.2))
# ms$calculate_spectra_charges(Settings_calculate_spectra_charges_StreamFind(roundVal = 15, relLowCut = 0.2, absLowCut = 8000))
# ms$deconvolute_spectra(Settings_deconvolute_spectra_StreamFind())
# ms$smooth_spectra(Settings_smooth_spectra_movingaverage(windowSize = 15))
# ms$normalize_spectra(Settings_normalize_spectra_minmax()) #liftTozero = TRUE
# ms$normalize_spectra(Settings_normalize_spectra_blockweight())
# ms$bin_spectra(Settings_bin_spectra_StreamFind(bins = list("rt" = 2, "mass" = 25), refBinAnalysis = 1))

# View(ms$spectra)
# ms$plot_spectra()
# ms$spectra_charges
# ms$plot_spectra_charges()
# ms$correct_spectra_baseline(Settings_correct_spectra_baseline_baseline())
# ms$plot_deconvoluted_spectra()
# ms$plot_spectra(interactive = T)
# ms$plot_spectra_charges()
# ms$spectra_charges
# ms$deconvoluted_spectra
# ms$spectra_charges
# ms$plot_spectra_charges()
# ms$get_spectra()
# ms$spectra
# ms$has_results("spectra")
# ms$spectra
# ms$plot_spectra(interactive = T)
# View(ms$get_results("spectra"))
```

Below we create an ordered list of *ProcessingSettings* objects for each processing method to be applied and add the list to the engine. The exact parameters for each method can be optimized individually by calling the specific method directly. Once the settings are added, the workflow can be inspected with the `print_workflow()` method.

```{r}
ms_workflow_settings <- list(
  Settings_cluster_spectra_StreamFind(val = "mz", clustVal = 0.01, presence = 0.2),
  Settings_calculate_spectra_charges_StreamFind(roundVal = 15, relLowCut = 0.2, absLowCut = 8000),
  Settings_deconvolute_spectra_StreamFind(),
  Settings_smooth_spectra_movingaverage(windowSize = 15),
  Settings_bin_spectra_StreamFind(bins = list("rt" = 5, "mass" = 20), refBinAnalysis = 1),
  Settings_average_spectra_StreamFind(),
  Settings_normalize_spectra_minmax(),
  Settings_normalize_spectra_blockweight()
)

@@

```{r}
raman_workflow_settings <- list(
  Settings_bin_spectra_StreamFind(unitsVal = "rt", unitsNumber = 3),
  Settings_normalize_spectra_minmax(),
  Settings_subtract_spectra_section_StreamFind(sectionWindow = c(0, 3)),
  Settings_smooth_spectra_savgol(fl = 21, forder = 4, dorder = 0),
  Settings_delete_spectra_section_StreamFind(list("shift" = c(-100, 330))),
  Settings_delete_spectra_section_StreamFind(list("shift" = c(1800, 2600))),
  Settings_correct_spectra_baseline_airpls(lambda = 45, differences = 1, itermax = 30),
  Settings_delete_spectra_section_StreamFind(list("rt" = c(0, 5.5))),
  Settings_delete_spectra_section_StreamFind(list("rt" = c(8, 11))),
  Settings_average_spectra_StreamFind(collapseTime = TRUE),
  Settings_normalize_spectra_minmax(),
  Settings_normalize_spectra_blockweight()
)

>>>>

The individual processing steps are applied according to *ProcessingStep*. Below, the integration of the TIC is shown using the dedicated *ProcessingStep* after loading the TIC chromatograms from the analysis files and smoothing using a moving average approach.

@@

```{r}
# Smoothing of the TIC chromatogram for improving peak finding
ms$smooth_chromatograms(Method_smooth_chromatograms_movingaverage(windowSize = 5))
```

```{r}
# Settings for integration of the TIC
ps_ic <- Method_integrate_chromatograms_StreamFind(
  merge = TRUE,
  closeByThreshold = 5,
  minPeakHeight = 3E6,
  minPeakDistance = 3,
  minPeakWidth = 20,
  maxPeakWidth = 200,
  minSN = 5
)

@@

According to the MS1 spectra, the *m/z* from 1200 to 2000 can be added to the dedicated *ProcessingStep* for deconvolution, as shown below. The first step is to load from the mzML files the traces within the retention time and *m/z* ranges selected.

@@

# ms$cluster_spectra(Method_cluster_spectra_StreamFind(val = "mz", clustVal = 0.01, presence = 0.2))
# ms$calculate_spectra_charges(Method_calculate_spectra_charges_StreamFind(roundVal = 15, relLowCut = 0.2, absLowCut = 8000))
# ms$deconvolute_spectra(Method_deconvolute_spectra_StreamFind())
# ms$smooth_spectra(Method_smooth_spectra_movingaverage(windowSize = 15))
# ms$normalize_spectra(Method_normalize_spectra_minmax()) #liftTozero = TRUE
# ms$normalize_spectra(Method_normalize_spectra_blockweight())
# ms$bin_spectra(Method_bin_spectra_StreamFind(bins = list("rt" = 2, "mass" = 25), refBinAnalysis = 1))

# View(ms$spectra)
# ms$plot_spectra()
# ms$spectra_charges
# ms$plot_spectra_charges()
# ms$correct_spectra_baseline(Method_correct_spectra_baseline_baseline())
# ms$plot_deconvoluted_spectra()
# ms$plot_spectra(interactive = T)
# ms$plot_spectra_charges()
# ms$spectra_charges
# ms$deconvoluted_spectra
# ms$spectra_charges
# ms$plot_spectra_charges()
# ms$get_spectra()
# ms$spectra
# ms$has_results("spectra")
# ms$spectra
# ms$plot_spectra(interactive = T)
# View(ms$get_results("spectra"))
```

Below we create an ordered list of *ProcessingStep* objects for each processing method to be applied and add the list to the engine. The exact parameters for each method can be optimized individually by calling the specific method directly. Once the settings are added, the workflow can be inspected with the `print_workflow()` method.

```{r}
ms_workflow_settings <- list(
  Method_cluster_spectra_StreamFind(val = "mz", clustVal = 0.01, presence = 0.2),
  Method_calculate_spectra_charges_StreamFind(roundVal = 15, relLowCut = 0.2, absLowCut = 8000),
  Method_deconvolute_spectra_StreamFind(),
  Method_smooth_spectra_movingaverage(windowSize = 15),
  Method_bin_spectra_StreamFind(bins = list("rt" = 5, "mass" = 20), refBinAnalysis = 1),
  Method_average_spectra_StreamFind(),
  Method_normalize_spectra_minmax(),
  Method_normalize_spectra_blockweight()
)

@@

```{r}
raman_workflow_settings <- list(
  Method_bin_spectra_StreamFind(unitsVal = "rt", unitsNumber = 3),
  Method_normalize_spectra_minmax(),
  Method_subtract_spectra_section_StreamFind(sectionWindow = c(0, 3)),
  Method_smooth_spectra_savgol(fl = 21, forder = 4, dorder = 0),
  Method_delete_spectra_section_StreamFind(list("shift" = c(-100, 330))),
  Method_delete_spectra_section_StreamFind(list("shift" = c(1800, 2600))),
  Method_correct_spectra_baseline_airpls(lambda = 45, differences = 1, itermax = 30),
  Method_delete_spectra_section_StreamFind(list("rt" = c(0, 5.5))),
  Method_delete_spectra_section_StreamFind(list("rt" = c(8, 11))),
  Method_average_spectra_StreamFind(collapseTime = TRUE),
  Method_normalize_spectra_minmax(),
  Method_normalize_spectra_blockweight()
)
